Homework

### 2016-07-06 Macro Impacts Revised.tex
Answers that make sense!!!
I think we’ve got good stuff here.

$\Delta r$ is the length of the tail, and $r_0$ is its base. $\bar p$ is the peak pressure of the shock, and we can take it to be the stress corresponding to the elastic limit of rock. It is reasonable to say that $\Delta r$ should be within an order of magnitude of $r_X$. The total energy of this pressure wave is

@@

>>>>

$\Delta r$ is the length of the tail, and $r_0$ is its base. $\bar p$ is the peak pressure of the shock, and we can take it to be the stress corresponding to the elastic limit of rock. The total energy of this pressure wave is

@@

Reviewing a USGS document (Rock Failure and Earthquakes) suggests that $\bar p$ be set at $10^8$. To calculate $\Delta r$, notice that the Earth is initially displaced by $r_X$. The Earth will then collapse back into the hole due to ambient pressure at the speed of sound $\alpha$, yielding a time of collapse $r_X/\alpha$. The speed of the shockwave initially produced by the object is approximately the speed of the object itself. Hence $\Delta r/v_X=r_X/\alpha$. Thus $\Delta r\approx\f{v_X}{\alpha}r_X$.
The following are the approximate quantities used
h&=1.2\times 10^7\te{m}\,,\\
v_X&=2.5\times 10^6\te{m s}^{-1}\,,\\
\rho_{\oplus}&=6\times 10^3\te{kg m}^{-3}\,,\\
\sigma_X&=10^{-11}\te{m}^2\,,\\
\abs{\td{E}{x}{}}&=\rho_{\oplus}\sigma_X v_X^2=3.75\times 10^5\te{J m}^{-1}\,,\\
E_{\te{total}}&=4.5\times 10^{12}\te{J}\,,\\
r_X&=1.8\times 10^{-6}\te{m}\,,\\
\alpha&=6\times 10^3\te{m s}^{-1}\,,\\
\beta&=3.5\times 10^{3}\te{m s}^{-1}\,,\\
\mu&=7.2\times 10^{10}\te{Pa}\,,\\
\lambda&=7.2\times 10^{10}\te{Pa}\,,\\
K&=1.2\times 10^{11}\te{Pa}\,.
These lead to the results
\Delta r&=7.4\times 10^{-4}\te{m}\,,\\
r_0&=1.6\times 10^3\te{m}\,,\\
E_{\te{propagated}}&=\f{8\times 10^{13}\te{J m}^2}{\lambda_0^2}\,,\\
\Xi&=\f{17.6\te{m}^2}{\lambda_0^2}\,.
Conservatively we set $\lambda_0$ at about $6$ kilometers. This yields a total suppression factor of $\Xi=4.9\times 10^{-7}$. Keep in mind that this estimate is incredibly conservative, and does not take into account any non-conservative processes in the nonlinear regime $r<r_0$. Note, even though both $\lambda_0$ and $r_0$ are on the same order of magnitude, the approximations used are still good since they are overestimates of the Bessel $J$ and Struve $H$ functions.
